Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-20 doc/PRF2022/PRF_main.tex
yny 0720 3

The governing equation for $u(\xx,t)$ is obtained by computing the domain variation of the free energy $F$ \cite{Fu2018_SIAM}:
We obtain
a screened Laplace equation boundary value problem as a model for the hydrophobic interaction between water and JPs:
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ gives the degree of hydrophobicity the
particle-solvent interface.

>>>>

The governing equation for $u(\xx,t)$ is obtained by computing the domain variation of the free energy $F$ \cite{Fu20}:
We obtain
a screened Laplace equation boundary value problem as a model for the hydrophobic interaction between water and JPs:
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ gives the degree of hydrophobicity the
particle-solvent interface.
